---
title: "SES Round 1 (not pilot)"
author: "Benny deMayo"
date: "1/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(png)
library(knitr)
library(markdown)
library(lmerTest)
library(ggthemes)
library(psych)
library(magrittr)
library(langcog)
library(tidyboot)
library(fs)
library(zipcode)
library(ggmap)
library(lubridate)

source(path(here::here(), "file_paths.R"))
```

Our aim here is to take a closer look at the data obtained in the latest round of WebCDI data collection. We will specifically be conmparing this batch to the initial data we collected when first using Facebook to diversify the sample. This code will have a lot of unnecessary redundancy with `ses_pilot_1.Rmd` but everyone will just have to deal with it.

```{r}
#accepts: path to directory of WebCDI summary score files
#returns: aggregated cleaned data
readInWebCDI <- function(directory) {
  clean_data <- 
    directory %>% 
    map_df(~read_csv(., col_types = cols(.default = col_character()))) %>% #read in columns as a character
    mutate_at(
      .funs = ~case_when(
        str_detect(., "<") ~ 1, #get rid of entries that have 'less than' signs in them
        TRUE ~ as.numeric(.)
      ),
      .vars = vars(contains("Percentile"))
    ) %>% 
    mutate_at(
      .funs = ~as.numeric(.), #turn all the quantitative columns back into numeric
      .vars = 
       vars(
          which(colnames(.) == "benchmark age"):ncol(.)
        )
    )
    return(clean_data)
}

ses_pilot_raw <- readInWebCDI(ses_pilot_directory)
ses_round_1_wg <- readInWebCDI(ses_round_1_wg_path)
ses_round_1_ws <- readInWebCDI(ses_round_1_ws_path)

```

Great, now the data is read in. We need to filter out participants now based on several criteria: birth weight, exposure to languages other than English, people who did the study too quickly.

First let's do the kids who were born prematurely or underweight:

```{r}

filterMultilingual <- function(data) {
  clean_data <- 
    data %>% 
    mutate_at(
      .vars = c("due_date_diff", "birth_weight_lb"),
      .funs = ~as.numeric(.)
    ) %>% 
    mutate_at(
      .vars = c("due_date_diff"),
      .funs = ~case_when(
        is.na(.) ~ 0, #turn non-NA's in this column into zeros
        TRUE ~ .
      )
    ) %>% 
    mutate(premature = due_date_diff >= 4 & birth_weight_lb < 5.5) %>% 
    filter(premature == FALSE)
  
  return(clean_data)
}

ses_pilot_raw <- ses_pilot_raw %>% filterMultilingual()
ses_round_1_wg <- ses_round_1_wg %>% filterMultilingual()
ses_round_1_ws <- ses_round_1_ws %>% filterMultilingual()

```

Now let's do kids who got a lot of exposure to languages other than English:

```{r}

filterMultilingual <- function(data) {
  clean_data <- 
    data %>% 
    mutate_at(
      .vars = c("language_days_per_week", "language_hours_per_day"),
      .funs = ~as.numeric(.)
    ) %>% 
    mutate(
      language_hours_per_week = language_days_per_week * language_hours_per_day
    ) %>% 
    filter(is.na(language_hours_per_week) | language_hours_per_week <= 16)
}

ses_pilot_raw <- ses_pilot_raw %>% filterMultilingual()
ses_round_1_wg <- ses_round_1_wg %>% filterMultilingual()
ses_round_1_ws <- ses_round_1_ws %>% filterMultilingual()


```


Now let's take care of the issue that some parents filled out the survey way too fast.

```{r}

ses_round_1_wg %>% 
  mutate(
    completion_interval = lubridate::interval(created_date, last_modified),
    completion_time = completion_interval / lubridate::minutes()
  )

getCompletionInterval <- function(data) {
  clean_data <- 
    data %>% 
    mutate(
      completion_interval = lubridate::interval(created_date, last_modified),
      completion_time = completion_interval / lubridate::minutes()
    )
  
  return(clean_data)
}

ses_round_1_wg <- ses_round_1_wg %>% getCompletionInterval
ses_round_1_ws <- ses_round_1_ws %>% getCompletionInterval

completion_times_round_1 <- 
  rbind(
    ses_round_1_wg %>% 
      select(study_name, subject_id, completion_time) %>% 
      mutate(study_name = "wg"),
    ses_round_1_ws %>% 
      select(study_name, subject_id, completion_time) %>% 
      mutate(study_name = "ws")
  ) 

completion_times_round_1 %>% 
  ggplot(aes(completion_time)) +
  geom_histogram(position = "dodge", binwidth = 5) +
  facet_wrap(~study_name) +
  coord_cartesian(xlim = c(0, 60)) +
  scale_x_continuous(breaks = seq(0, 60, 3))



```

Well, that looks like a problem...


