---
title: "Analysis round 1"
author: "Benny deMayo"
date: "5/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(png)
library(knitr)
library(markdown)
library(lmerTest)
library(ggthemes)
library(psych)
library(magrittr)
library(langcog)
library(tidyboot)
library(fs)
library(zipcode)
library(ggmap)

source(path(here::here(), "file_paths.R"))
```

##Reading and wrangling

Our goal here is to take a look at data from the first (messy) pilot of web-CDI specifically aimed at non-white, lower-SES samples.

First, we read in the data and do some minor cleaning jobs to it.

```{r}
ses_pilot_raw <- 
  ses_pilot_directory %>% 
  map_df(~read_csv(., col_types = cols(.default = col_character()))) %>% #read in columns as a character
  mutate_at(
    .funs = ~case_when(
      str_detect(., "<") ~ 1, #get rid of entries that have 'less than' signs in them
      TRUE ~ as.numeric(.)
    ),
    .vars = vars(contains("Percentile"))
  ) %>% 
  mutate_at(
    .funs = ~as.numeric(.), #turn all the quantitative columns back into numeric
    .vars = 
      vars(
        which(colnames(.) == "benchmark age"):ncol(.)
      )
  )



  
```

###Filtering out participants

####Exposure to a second language

First, we filter out children whose parents report exposure to a language other than English for more than 16 hours per week.

```{r}

ses_pilot_raw <- 
  ses_pilot_raw %>% 
  mutate_at(
    .vars = c("language_days_per_week", "language_hours_per_day"),
    .funs = ~as.numeric(.)
  ) %>% 
  mutate(
    language_hours_per_week = language_days_per_week * language_hours_per_day
  ) %>% 
  filter(is.na(language_hours_per_week) | language_hours_per_week <= 16)

```

Next, we filter out children who were both underweight at birth (<= 5 lbs 5 oz) and who were born prematurely (4 or more weeks before the due date).

```{r}

#ask about this to Mike because there should be a way to condense this code
ses_pilot_raw <- 
  ses_pilot_raw %>% 
  mutate_at(
    .vars = c("due_date_diff", "birth_weight_lb"),
    .funs = ~as.numeric(.)
  ) %>% 
  mutate_at(
    .vars = c("due_date_diff"),
    .funs = ~case_when(
      is.na(.) ~ 0, #turn non-NA's in this column into zeros
      TRUE ~ .
    )
  ) %>% 
  mutate(premature = due_date_diff >= 4 & birth_weight_lb < 5.5) %>% 
  filter(premature == FALSE)

```


Create different columns for the different ethnicities.

```{r}

ses_pilot_raw <- 
  ses_pilot_raw %>% 
  mutate( #get rid of brackets in ethnicity column
    child_ethnicity = str_replace_all(child_ethnicity, "[^[:upper:]]", "")
  ) %>% 
  mutate(
    ethnicity_white = str_detect(child_ethnicity, "W"),
    ethnicity_black = str_detect(child_ethnicity, "B"),
    ethnicity_asian = str_detect(child_ethnicity, "A"),
    ethnicity_native = str_detect(child_ethnicity, "N"),
    ethnicity_other = str_detect(child_ethnicity, "O"),
    ethnicity_mixed = str_length(child_ethnicity) > 1
  )

old_ethnicity_numbers <- 
  tibble(
    ethnicity = c("Asian", "Black", "Mixed", "White"),
    `2007 manual` = c(.069, .105, .063, .733)
  )

ses_pilot_ethnicity <- 
  ses_pilot_raw %>% 
  mutate( #get rid of brackets in ethnicity column
    child_ethnicity = str_replace_all(child_ethnicity, "[^[:upper:]]", "")
  ) %>%
  mutate(
    ethnicity = case_when(
      str_length(child_ethnicity) > 1 ~ "mixed",
      TRUE ~ child_ethnicity
    ) %>% fct_recode(
      Asian = "A",
      Black = "B",
      Mixed = "mixed",
      White = "W"
    )
  ) %>% 
  filter(ethnicity != "") %>% 
  select(subject_id, child_ethnicity, ethnicity) %>% 
  count(ethnicity) %>% 
  mutate(`Current study` = n / sum(n)) %>% 
  left_join(
    old_ethnicity_numbers,
    by = c("ethnicity")
  ) %>% 
  pivot_longer(
    cols = c(`Current study`, `2007 manual`),
    names_to = "study",
    values_to = "proportion"
  )

ses_pilot_ethnicity %>% 
  ggplot(aes(ethnicity, proportion, fill = study)) +
  geom_col(position = "dodge") +
  labs(
    x = "Ethnicity",
    y = "Proportion of respondents"
  ) +
  theme_few() +
  theme(legend.title = element_blank()) 


```

2007 numbers:
White: 73.3
Black: 10.5
Asian: 6.9
Mixed: 6.3
(order them in this order)

```{r}

#make a dataframe to plot ethnicity statistics
ethnicity_demographics <- 
  ses_pilot_raw %>% 
  summarize_at(
    .vars = vars(starts_with("ethnicity")),
    .funs = ~ mean(., na.rm = TRUE)
  ) %>% 
  gather(key = "ethnicity", value = "proportion", everything()) %>% 
  mutate(ethnicity = str_replace(ethnicity, "ethnicity_", ""))

ethnicity_demographics %>% 
  ggplot(aes(reorder(ethnicity, -proportion), proportion)) +
  geom_col() +
  labs(
    x = "ethnicity"
  )
```

Next we look at maternal education statistics.

```{r}

#get rid of text in education columns
ses_pilot_raw <- 
  ses_pilot_raw %>% 
  mutate_at(
    .vars = vars(contains("education")),
    .funs = function(ed_value) {
      print(ed_value)
      num_years_ed <- 
        ed_value %>% 
        str_replace_all("[^[:digit:]|\\.]", "") %>% 
        as.numeric() 
      
      return(num_years_ed)
    }
  ) %>% 
  mutate(age = as.numeric(age))

maternal_ed <- 
  ses_pilot_raw %>% 
  select(subject_id, mother_education) %>% 
  mutate(
    maternal_ed = case_when(
      mother_education <= 11 ~ "Some high school or less",
      mother_education == 12 ~ "High school diploma",
      mother_education %in% seq.int(13, 15) ~ 
        "Some college education",
      mother_education >= 16 ~ "College diploma or more"
    )
  )

old_props <- 
  tibble(
    maternal_ed = c(
      "Some high school or less",
      "High school diploma",
      "Some college education",
      "College diploma or more"
    ),
    `2007 manual` = c(.075, .2385, .248, .4385)
  )

maternal_ed %>% 
  count(maternal_ed) %>% 
  mutate(
    `Current study` = n / sum(n)
  ) %>% 
  left_join(old_props, by = c("maternal_ed")) %>% 
  select(-n) %>% 
  pivot_longer(
    cols = c("Current study", "2007 manual"), 
    names_to = "Study type", 
    values_to = "proportion"
  ) %>% 
  mutate(
    maternal_ed = fct_relevel(
      maternal_ed,
      "Some high school or less",
      "High school diploma",
      "Some college education",
      "College diploma or more"
    )
  ) %>% 
  ggplot(aes(maternal_ed, proportion, fill = `Study type`)) +
  geom_col(position = "dodge") +
  labs(
    x = "Education Level",
    y = "Proportion of respondents"
  ) +
  theme_few() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 10, vjust = 0.9, hjust = 1, size = 8),
    axis.title.x = element_text()
  ) 
```


Scatter plot of words understood vs. age
```{r}

ses_pilot_raw %>% 
  ggplot(aes(age, `Words Understood`)) +
  geom_point() +
  geom_smooth(method = "loess")

ses_pilot_raw %>% 
  ggplot(aes(age, `Words Produced`)) +
  geom_point() 

ses_pilot_raw %>% 
  ggplot(aes(mother_education, `Words Understood`)) +
  geom_point()

ses_pilot_raw %>% 
  ggplot(aes(mother_education)) +
  geom_histogram()

```


```{r}

ses_pilot_raw %>% 
  count(sex)

ses_pilot_raw %>% 
  count(child_hispanic_latino)

mean(ses_pilot_raw$`Words Produced Percentile-both`)
mean(ses_pilot_raw$`Words Understood Percentile-both`)
```


```{r}
data("zipcode")

zip_code_data <- read_csv(zip_code_path)

three_digit_avg <- 
  zipcode %>% 
  mutate(prefix = str_sub(zip, 1, 3)) %>% 
  group_by(prefix) %>% 
  summarize(
    mean_lat = mean(latitude, na.rm = TRUE),
    mean_long = mean(longitude, na.rm = TRUE)
  ) %>% 
  ungroup()

ses_pilot_zips <- 
  ses_pilot_raw %>% 
  mutate(zip_code = str_replace_all(zip_code, "[^[:digit:]]", "")) %>% 
  left_join(
    three_digit_avg,
    by = c("zip_code" = "prefix")
  ) %>% 
  select(subject_id, mean_lat, mean_long)

ses_pilot_cities <- 
  ses_pilot_raw %>% 
  mutate(zip_code = str_replace_all(zip_code, "[^[:digit:]]", "")) %>% 
  mutate(zip_code = as.numeric(zip_code)) %>% 
  left_join(
    zip_code_data,
    by = c("zip_code" = "ZIP prefix")
  ) %>% 
  select(subject_id, zip_code, `City`)

usa_center <- as.numeric(geocode("United States"))

usa_map <- 
  get_googlemap(center = usa_center, scale = 2, zoom = 4) %>% 
  ggmap()

usa_map

usa_map +
  geom_point(
    aes(x = mean_long, y = mean_lat), 
    data = ses_pilot_zips,
    size = .7,
    alpha = 0.7
  )

ses_pilot_zips %>% 
  qmplot(x = mean_long, y = mean_lat)
 
```


```{r}
#zip code data

prefixes <- read_csv(zip_prefix_path)

ses_pilot_prefixes <- 
  ses_pilot_raw %>% 
  mutate(zip_code = str_replace_all(zip_code, "[^[:digit:]]", "")) %>% 
  mutate(zip_code = as.numeric(zip_code)) %>% 
  select(subject_id, zip_code) %>%
  left_join(
    prefixes,
    by = c("zip_code" = "prefix")
  )

state_breakdown <- 
  ses_pilot_prefixes %>% 
  count(state) 

View(ses_pilot_prefixes %>% 
  count(distribution_center, state) %>% 
  arrange(-n))


```

